Size matters: Divergent morphology in elliptical bifaces from sites in the American Southeast articulates with distinct local reduction practices

### 2022-08-23 supp/index.Rmd
<edit index>

American Southeast, Caddo, Jowell biface, lithics, archaeology, archaeoinformatics, museum studies, digital humanities, geometric morphometrics, STEM, STEAM

@@

knitr::include_graphics('./images/ellipticalbifaces.jpg')
```

>>>>

American Southeast, Caddo, archaeology, anthroinformatics, archaeoinformatics, museum studies, digital humanities, geometric morphometrics, STEM, STEAM, Jowell biface, lithics, parallel-oblique flaking

@@

knitr::include_graphics('./images/ellipticalbifaces.png')
```
